Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-07-09 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

To establish the essential optimality of Algorithm \ref{DHKM:TrackConeAlg} requires some additional, reasonable assumptions on the sequences $(n_j)_{j \in \N_0}$ and $\bigl(\sigma_j(f) \bigr)_{j \in \N_0}$.  Recall from \eqref{DHKM:NormLambdaFinite} that $\bigl(\Lambda_j \bigr)_{j \in \N_0}$ has a finite $\rho'$ norm.  We require that the $\Lambda_j$ must decay steadily with $j$:
\begin{equation} \label{DHKM:LambdaDecayCond}
    \alpha^{-1} \beta^r \Lambda_j \le \Lambda_{j+r} \le \alpha \gamma^r \Lambda_j  \quad \forall j,r \in \N_0, \qquad \text{for some } \beta, \gamma < 1 \le \alpha.
\end{equation}
We also assume that the ratio of the largest to smallest $\lambda_{\bsk}$ in a group is bounded above:
\begin{equation} \label{DHKM:MinMaxCond}
    \sup_{j \in \N} \frac{\lambda_{\bsk_{n_{j-1}+1}}}{\lambda_{\bsk_{n_{j}}}} \le S_1 < \infty.
\end{equation}
For the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.  Let $\card(\cdot)$ denote the cardinality of a set. We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le n_{j+1}$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements: 
\begin{equation} \label{DHKM:PropCond}
     \inf_{j \in \N} \ \min_{\calJ \subset \bbK \, : \, \card(\calJ) \le n_j} \ \max_{0 \le l \le j+1} \frac{\card(\calK_l \setminus \calJ)}{\card(\calK_l)} \ge S_2 > 0.
\end{equation}
Again, for the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.

>>>>

To establish the essential optimality of Algorithm \ref{DHKM:TrackConeAlg} requires some additional, reasonable assumptions on the sequences $(n_j)_{j \in \N_0}$ and $\bigl(\sigma_j(f) \bigr)_{j \in \N_0}$.  Recall from \eqref{DHKM:NormLambdaFinite} that $\bigl(\Lambda_j \bigr)_{j \in \N_0}$ has a finite $\rho'$ norm.  We require that the $\Lambda_j$ must decay steadily with $j$:
\begin{equation} \label{DHKM:LambdaDecayCond}
    \alpha^{-1} \beta^r \Lambda_j \le \Lambda_{j+r} \le \alpha \gamma^r \Lambda_j  \quad \forall j,r \in \N_0, \qquad \text{for some } \beta, \gamma < 1 \le \alpha.
\end{equation}
We also assume that the ratio of the largest to smallest $\lambda_{\bsk}$ in a group is bounded above:
\begin{equation} \label{DHKM:MinMaxCond}
    \sup_{j \in \N} \frac{\lambda_{\bsk_{n_{j-1}+1}}}{\lambda_{\bsk_{n_{j}}}} \le S_1 < \infty.
\end{equation}
For the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.  Let $\card(\cdot)$ denote the cardinality of a set. We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le \DHKMchange{j+1}$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements: 
\begin{equation} \label{DHKM:PropCond}
     \inf_{j \in \N} \ \min_{\calJ \subset \bbK \, : \, \card(\calJ) \le n_j} \ \max_{0 \le l \le j+1} \frac{\card(\calK_l \setminus \calJ)}{\card(\calK_l)} \ge S_2 > 0.
\end{equation}
Again, for the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.
